Hydra Battles and Cie

### 2021-02-10 doc/hydras.tex
comments and examples about the Ackermann part (to continue)
add an exercise
creation of a multiple index
work on the index

\documentclass[a4paper]{book}
\usepackage{alltt}
\usepackage{makeidx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\setcounter{tocdepth}{1}
\input{coqmacros}

@@

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, Bordeaux-INP\\with contributions by Yves Bertot, \'Evelyne Contejean,  Florian Hatat and Pascal Manoury\\ \emph{The formalization of primitive recursive functions was originally authored by Russel O'Connor}}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex
\begin{document}
\maketitle

@@

\index{Coq!Commands!Print Assumptions}

@@

@@

\begin{todo}
 Still very incomplete!
\end{todo}

\printindex

@@

Ord & countable ordinals (after Schütte) & \pageref{types:Ord} \\
ppT1 & pretty printed version of T1 & \pageref{types:ppT1} \\
SubON & comparison of ordinal notations & \pageref{types:SubON} \\
T1 & ordinal terms below $\epsilon_0$ & \pageref{types:T1} \\
T2 & ordinal terms below $\Gamma_0$ & \pageref{types:T2} \\
WO & well orders (Schütte's definition) & \pageref{types:WO} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main functions and constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina & Math & Description & Page \\ \hline
canon & canon alpha i & $\canonseq{\alpha}{i}$& Canonical sequence & \pageref{Functions:canon}\\
canonS & canonS alpha i & $\canonseq{\alpha}{i+1}$& Helper for canon & \pageref{Functions:canonS}\\
F\_ & F\_ alpha n & $F_\alpha(n)$ & Wainer's \texttt{F} fast growing hierarchy & \pageref{Functions:F-alpha} \\
H\_ & H\_ alpha n & $H_\alpha(n)$ & Hardy's \texttt{H} fast growing hierarchy & \pageref{Functions:H-alpha} \\
iterate & iterate $f$ $n$ $x$ & $f^{(n)}(x)$ & Functional iteration & \pageref{Functions:iterate} \\
L\_ & L\_ alpha k & $L_\alpha(k)$ & final step of a standard path & \pageref{Functions:L-alpha} \\
succ & succ alpha & & Successor & \pageref{Functions:succ-T1}, \pageref{Functions:succ-sch} \dots \\
zero:Ord & & $0$ & The least ordinal (Schütte's model) & \pageref{Constants:zero:Ord} \\

\hline
\end{tabular}
\end{threeparttable}
\end{table}

>>>>

\documentclass[a4paper]{book}
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\setcounter{tocdepth}{1}
\input{coqmacros}

@@

\author{Pierre Castéran\\ LaBRI, Univ. Bordeaux, CNRS UMR 5800, Bordeaux-INP\\with contributions by Yves Bertot, \'Evelyne Contejean,  Florian Hatat and Pascal Manoury\\ \emph{The formalization of primitive recursive functions was originally authored by Russel O'Connor}}
\date{\today}
\title{Hydra Battles and Cie}
\makeindex{coq}
\makeindex{maths}
\makeindex{hydras}
\makeindex{additions}
\makeindex{primrec}
\begin{document}
\maketitle

@@

\index{coq}{Commands!Print Assumptions}

@@

Please consult the sub-directory \texttt{exercises/} of the
 project (in construction).

@@

% \begin{todo}
%  Still very incomplete!
% \end{todo}

\printindex{coq}{Coq, plug-ins and standard library}
\printindex{maths}{Mathematical notions and algorithmics}
\printindex{hydras}{Library hydras: Ordinals and hydra battles}
\printindex{primrec}{Library hydras.Ackermann: Primitive recursive functions}
\printindex{additions}{Library additions: Addition chains}

@@

ppT1 & pretty printed version of T1 & \pageref{types:ppT1} \\
SubON & comparison of ordinal notations & \pageref{types:SubON} \\
T1 & ordinal terms below $\epsilon_0$ & \pageref{types:T1} \\
T2 & ordinal terms below $\Gamma_0$ & \pageref{types:T2} \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main functions and constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Name & Gallina & Math & Description & Page \\ \hline
canon & canon alpha i & $\canonseq{\alpha}{i}$& Canonical sequence & \pageref{Functions:canon}\\
canonS & canonS alpha i & $\canonseq{\alpha}{i+1}$& Helper for canon & \pageref{Functions:canonS}\\
F\_ & F\_ alpha n & $F_\alpha(n)$ & Wainer's \texttt{F} fast growing hierarchy & \pageref{Functions:F-alpha} \\
H\_ & H\_ alpha n & $H_\alpha(n)$ & Hardy's \texttt{H} fast growing hierarchy & \pageref{Functions:H-alpha} \\
L\_ & L\_ alpha k & $L_\alpha(k)$ & final step of a standard path & \pageref{Functions:L-alpha} \\
succ & succ alpha & & Successor & \pageref{Functions:succ-T1}, \pageref{Functions:succ-sch} \dots \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}
